---
title: "Journal (reproducible report)"
author: "Marvin Gravert"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post
Basically the first challenge can be solved by copying the busines case example. Not much more involved. For ease of use the data has been copied into the folder challenge_1 in the repo.
## First the data is "wrangeld"
```{r}
library(tidyverse)

# 2.0 Importing Files ----
bikes=readxl::read_excel("challenge_1/bikes.xlsx")
bikeshops=readxl::read_excel("challenge_1/bikeshops.xlsx")
order_lines=readxl::read_excel("challenge_1/orderlines.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl=left_join(order_lines, bikes, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops, by=c("customer.id"="bikeshop.id"))
# 5.0 Wrangling Data ----
bike_orderlines_joined_tbl %>% 
  separate(col=category, into=c("product_family","cat2","cat3"),sep=" - ")%>%
  select(-c("gender","url","...1"))%>%
  mutate(total_price=price*quantity) %>%
  select(-ends_with(".id"))%>%
  bind_cols(bike_orderlines_joined_tbl%>%select(order.id))%>%
  select(order.id,contains("order"),total_price,everything())%>%
  rename(bikeshop=name)%>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))->
  bike_orderlines_wrangled_tbl
# 6.0 Business Insights ----
# 6.3 Sales by State
bike_orderlines_wrangled_tbl %>%
  separate(col=location, into=c("city","state"),sep=", ")%>%
  select(total_price, state)%>%
  group_by(state)%>%
  summarise(sales=sum(total_price))%>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                    decimal.mark = ",",
                                    prefix = "",
                                    suffix = " €"))->
  sales_by_state_tbl
```
## Plots 
At first the simple state sales distribution plot
```{r plot, fig.width=10, fig.height=7}
sales_by_state_tbl%>%
  ggplot(aes(x=state, y=sales)) +
  geom_col()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_label(aes(label=sales_text))+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )
```
And finally the more complex state-year sales distribution plot
```{r plot2, fig.width=10, fig.height=7}
# 6.4 Sales by State and City
bike_orderlines_wrangled_tbl %>%
  separate(col=location, into=c("city","state"),sep=", ")%>%
  select(total_price,state,order_date)%>%
  mutate(year=lubridate::year(order_date))%>%
  group_by(state,year)%>%
  summarize(sales=sum(total_price))%>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",",
                                     prefix = "",
                                     suffix = " €"))->
  sales_by_state_and_year_tbl

# Visualization
sales_by_state_and_year_tbl %>%
    ggplot(aes(x=year, y=sales, fill=state))+
    geom_col()+
    facet_wrap(~state)+
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                      decimal.mark = ",",
                                                      prefix = "",
                                                      suffix = " €")) +
    labs(
      title = "Revenue by year and state category",
      fill = "State" # Changes the legend name
    )
```
Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.