---
title: "Journal (reproducible report)"
author: "Marvin Gravert"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Intro into tidyverse Challenge
Basically the first challenge can be solved by copying the business case example. Not much more involved. For ease of use the data has been copied into the folder challenge_1 in the repo.
## First the data is "wrangeld"
```{r}
library(tidyverse)

# 2.0 Importing Files ----
bikes=readxl::read_excel("challenge_1/bikes.xlsx")
bikeshops=readxl::read_excel("challenge_1/bikeshops.xlsx")
order_lines=readxl::read_excel("challenge_1/orderlines.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl=left_join(order_lines, bikes, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops, by=c("customer.id"="bikeshop.id"))
# 5.0 Wrangling Data ----
bike_orderlines_joined_tbl %>% 
  separate(col=category, into=c("product_family","cat2","cat3"),sep=" - ")%>%
  select(-c("gender","url","...1"))%>%
  mutate(total_price=price*quantity) %>%
  select(-ends_with(".id"))%>%
  bind_cols(bike_orderlines_joined_tbl%>%select(order.id))%>%
  select(order.id,contains("order"),total_price,everything())%>%
  rename(bikeshop=name)%>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))->
  bike_orderlines_wrangled_tbl
# 6.0 Business Insights ----
# 6.3 Sales by State
bike_orderlines_wrangled_tbl %>%
  separate(col=location, into=c("city","state"),sep=", ")%>%
  select(total_price, state)%>%
  group_by(state)%>%
  summarise(sales=sum(total_price))%>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                    decimal.mark = ",",
                                    prefix = "",
                                    suffix = " €"))->
  sales_by_state_tbl
```
## Plots 
At first the simple state sales distribution plot
```{r plot, fig.width=10, fig.height=7}
sales_by_state_tbl%>%
  ggplot(aes(x=state, y=sales)) +
  geom_col()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_label(aes(label=sales_text))+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )
```
And finally the more complex state-year sales distribution plot
```{r plot2, fig.width=10, fig.height=7}
# 6.4 Sales by State and City
bike_orderlines_wrangled_tbl %>%
  separate(col=location, into=c("city","state"),sep=", ")%>%
  select(total_price,state,order_date)%>%
  mutate(year=lubridate::year(order_date))%>%
  group_by(state,year)%>%
  summarize(sales=sum(total_price))%>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",",
                                     prefix = "",
                                     suffix = " €"))->
  sales_by_state_and_year_tbl

# Visualization
sales_by_state_and_year_tbl %>%
    ggplot(aes(x=year, y=sales, fill=state))+
    geom_col()+
    facet_wrap(~state)+
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                      decimal.mark = ",",
                                                      prefix = "",
                                                      suffix = " €")) +
    labs(
      title = "Revenue by year and state category",
      fill = "State" # Changes the legend name
    )
```

# Data aquisition Challenge

This challenge is seperated into two individual tasks, API-querying and webscraping.

## API

The first part of the challenge requried to query an API. Initially I wanted to query spotify but unfortunately the `spotifyr` library hasn't been released yet for my version of R. Twitter API required answers to too many questions and the reddit API was a bit slow, so eventually I settled to just querying the weather in Hamburg at the TUHH. This was done using the [openweathermap](https://home.openweathermap.org/ )
The GPS coordinate of the TUHH are roughly lat=53.461 lon=9.96922643.
Besides the current temperature the API also returns a "feels like" temperature, which I found a rather interesting bit of data.

```{r}
library(tidyverse)
library(httr)
library(glue)
library(jsonlite)
###Calling API
base_url="api.openweathermap.org/data/2.5/weather"
endpoint=glue("{base_url}?lat=53.461&lon=9.96922643&appid={Sys.getenv('WEATHER_API')}")
GET(endpoint)%>%
  .$content%>%
  rawToChar()%>%
  fromJSON()->weather_data
# Kelvin to Celsius
K_TO_C=function(temperature){
  temperature-273.15 
}
# current temp
weather_data$main$temp->t
cat("Current Temperature: ",K_TO_C(t),"C")
# though the temperature feels like
weather_data$main$feels_like->t
cat("Though it feels like: ", K_TO_C(t),"C")
```

## Web scraping

For this rosebikes is scraped. I decided to only scrape on category as its simpler and no real insight is gained by scraping all categories. As the resulting tibble only has 9 entries the `head` function is not required. 
```{r}
library(stringr)
library(rvest)
base_url="https://www.rosebikes.de/"
base_url%>% 
  read_html()%>%
  html_nodes(".main-navigation-category-with-tiles__link")%>%
  html_attr("href")%>%
  str_remove("\\/")%>%
  enframe(name="position", value="link")%>%
  mutate(url=glue("{base_url}{.$link}"))->
  bike_category_url_tbl

test=bike_category_url_tbl$url[1]
html_bike_category=read_html(test)
html_bike_category%>%
  html_nodes(".catalog-category-bikes__title-text")%>%
  html_text()%>%
  str_remove_all("\\n")%>%
  enframe(name="position",value="name")->
  bike_name_single_category

html_bike_category%>%
  html_nodes(".catalog-category-bikes__price-title")%>%
  html_text()%>%
  str_remove_all("\\n")%>%
  str_remove_all("ab")%>%
  str_remove_all("€")%>%
  str_remove_all("\\s")%>%
  str_remove("\\.")%>%
  str_replace("\\,","\\.")%>%
  as.numeric(.)%>%
  enframe(name="position", value="price")->
  bike_price_single_category
left_join(bike_name_single_category,bike_price_single_category)

```

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.